The Impact of Subway Systems on Air Pollution

### 2023-02-24 Paper Two .qmd
new

## Analysis Tool
The data will be presented clearly and succinctly with these visuals, making it simpler to comprehend the relation between air pollution and subway. This following analysis is processed in R @R  with packages of tidyverse(@tidyverse), dplyr(@dplyr). The tables is constructed via knitr(@knite). The package inside of tidyverse helps to create the plots via ggplot2(@tidyverse). This paper is knitted as PDF file by the packages of R markdown (@RMarkdown).

@@

The study used satellite imagery to measure the concentration of particulates in the air. The study uses data from satellites to measure the aerosol optical depth (AOD) of the atmosphere at a 3km spatial resolution. The Moderate Resolution Imaging Spectrometers on Terra and Aqua earth-observing satellites provide daily AOD measures. The satellite data was collected from the NASA MODIS instrument, which provides measurements of particulate matter at a resolution of 10 kilometers. The satellite data was then combined with ground-based measurements of particulate matter to create a comprehensive dataset that could be used to analyze the impact of subway systems on air pollution. (@Remer, L. A., S. Mattooand R. C. Levy, and L. A. Munchak. 2013. Modis 3km aerosol product: algorithm and global perspective. Atmospheric Measurement Techniques 6: 1829--1844.)

@@

kable(head(subway_data,5), caption = "Subway City (First 5 rows)")
```

@@

subway_data_monthly%>%group_by(Country)%>%summarise(Total=sum(as.numeric(Ridership),na.rm=T))

subway_data_monthly%>%filter(Country=="Chile")
```

@@

```{r ,fig.width= 15,fig.height= 20,warning = FALSE ,echo=FALSE,message=FALSE}
#| eval: true
#| warning: false
#| echo: false
#| label: fig-five
#| fig-cap: "Relation by year"

@@

>>>>

## Analysis Tool
The data will be presented clearly and succinctly with these visuals, making it simpler to comprehend the relation between air pollution and subway. This following analysis is processed in R @R  with packages of tidyverse @tidyverse, dplyr @dplyr. The tables is constructed via knitr @knitr. The package inside of tidyverse helps to create the plots via ggplot2 @tidyverse. This paper is knitted as PDF file by the packages of R markdown @RMarkdown.

@@

The study used satellite imagery to measure the concentration of particulates in the air. The study uses data from satellites to measure the aerosol optical depth (AOD) of the atmosphere at a 3km spatial resolution. The Moderate Resolution Imaging Spectrometers on Terra and Aqua earth-observing satellites provide daily AOD measures. The satellite data was collected from the NASA MODIS instrument, which provides measurements of particulate matter at a resolution of 10 kilometers. The satellite data was then combined with ground-based measurements of particulate matter to create a comprehensive dataset that could be used to analyze the impact of subway systems on air pollution @z.

@@

table <- subway_data %>%
  select(Country, Urbanname, Year, Ridership,ReferencePeriod)

kable(head(table,5), caption = "Subway City (First 5 rows)")
```

@@

new <- subway_data_monthly%>%group_by(Country)%>%summarise(Total=sum(as.numeric(Ridership),na.rm=T))%>%filter(Country=="Chile")

kable(head(subway_data_monthly,5), caption = "Subway City in Chile (First 5 rows)")
```

@@

```{r ,fig.width= 25,fig.height= 10,warning = FALSE ,echo=FALSE,message=FALSE}
#| eval: true
#| warning: false
#| echo: false
#| label: fig-five
#| fig-cap: "Relation by year"

@@

```{r,warning = FALSE ,echo=FALSE,message=FALSE}
subway_city <- read.csv(file = '/Users/lucas/Documents/paper2/subway_date_construction_begins_V2_AEJ_revision.csv')
```
